\begin{thebibliography}{9}

\bibitem{joepamer2011}
    Donna Malayeru, Joe Pamer, Don Syme.
    \emph{Strongly-Typed Language Supportfor an Information-Rich World}.
    Microsoft Corparation,
    2011.

\bibitem{gosuguide}
    \emph{Gosu Reference Guide}.
    Guidewire Software, Inc.
    Доступно по адресу \url{http://gosu-lang.org/doc/pdf/gosuref.pdf},
    2011.

\bibitem{bracha}
    Gilad Bracha.
    \emph{Pluggable Type Systems}.
    OOPSLA Workshop on revival of Dynamic Languages.
    2004.

\bibitem{pierce}
    Benjamin C. Pierce.
    \emph{Types and Programming Languages}.
    The MIT Press, 2002.

\bibitem{javacop2010}
    S. Markstrum, D. Marino, M. Esquivel, T. D. Millstein, C. Andreae, and J. Noble.
    \emph{JavaCOP:\@ Declarative pluggable types for Java}.
    ACM Trans. Program. Lang. Syst., 32(2), 2010.

\bibitem{checkerframework2008}
    Papi M., Ali M., Correa T.L., Perkins J., Ernst M.D..
    \emph{Practical Pluggable Types for Java}.
    ISSTA, Static Analysis, July 20–24, 2008.

\bibitem{strongtalk1993}
    Gilad Bracha, David Griswold.
    \emph{Strongtalk: Typechecking Smalltalk in a production environment}.
    Proceedings of the OOPSLA '93 Conference on Object-oriented Programming Systems, Languages and Applications, 1993.

\bibitem{newspeak2008}
    Gilad Bracha, Peter Ahe, Vassili Bykov, Eliot Miranda, Yaron Kashai.
    \emph{The Newspeak Programming Platform}.
    Cadence Design Systems.
    Доступно по адресу \url{http://bracha.org/newspeak.pdf},
    2008.

\bibitem{scala-spec}
    Martin Odersky.
    \emph{The Scala Language Specification}.
    Доступно по адресу \url{http://scala-lang.org/docu/files/ScalaReference.pdf},
    2011.

\bibitem{E4X}
    Standard ECMA-357
    ECMAScript for XML (E4X) Specification,
    2nd edition.
    Доступно по адресу \url{http://ecma-international.org/publications/files/ECMA-ST/Ecma-357.pdf},
    2005

\bibitem{scala-compiler-plugin}
    Anders Bach Nielsen
    \emph{Scala Compiler Phase and Plug-In Initialization for Scala 2.8}.
    Доступно по адресу \url{http://www.scala-lang.org/sites/default/files/sids/nielsen/Thu,%202009-05-28,%2008:13/compiler-phases-sid.pdf},
    2008.

\bibitem{extendible-c}
    `C Specification.
    Доступно по адресу \url{http://pdos.csail.mit.edu/~engler/pldi96-abstract.html}.

 \bibitem{metaml}
    Eugenio Moggi1 , Walid Taha2 , Zine El-Abidine Benaissa2, Tim Sheard.
    \emph{An Idealized MetaML: Simpler, and More Expressive}.
    Доступно по адресу \url{http://disi.unige.it/person/MoggiE/ftp/esop99.pdf},
    1999.

\bibitem{codecomplete}
    Steve McConnell. \emph{Code Complete, Second Edition}. Microsoft Press, Redmond, WA, USA, 2004.

\end{thebibliography}